---
title: "COVID-19 dashboard de Zdendulak"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}

# Load libraries

library(flexdashboard)
library(readr)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(plotly)
library(DT)

# Load constants

LIMIT_CASE <- 100
LIMIT_DEATH <- 10

LIMIT_CASE_RATE <- 1
LIMIT_DEATH_RATE <- 0.1

CASE_CUTOFF <- 1000
DEATH_CUTOFF <- 50
MAX_DAYS <- 40

# Load functions

plot_data <- function(data, date, var, n = 20, plotly = TRUE) {
  date_ <- date
  var <- enquo(var)
  
  g <- data %>% 
    filter(date == date_) %>% 
    top_n(n, !!var) %>% 
    ggplot(aes(y = reorder(country, !!var), x = !!var)) + 
    geom_bar(stat = "identity") +
    theme(axis.title.y=element_blank())
  
  if (plotly) {
    ggplotly(g)
  } else {
    g
  }
}

plot_trend <- function(data, xvar, yvar, xvar_max = NULL, plotly = TRUE) {
  xvar <- enquo(xvar)
  yvar <- enquo(yvar)
  
  g <- data %>% 
    filter(!!xvar != 0,
           !!xvar <= xvar_max) %>% 
    ggplot(aes(x = !!xvar, y = !!yvar, color = country)) + 
    geom_line() + scale_y_continuous(trans='log10')
  
  if (plotly) {
    ggplotly(g)
  } else {
    g
  }
}

top_countries <- function(data, n, var) {
  var <- enquo(var)
  
  data %>% 
    filter(date == latest_date) %>% 
    top_n(n, !!var) %>% 
    pull(country)
}

top_country_range <- function(data, n, m, var) {
  var <- enquo(var)
  
  if (n == 1) {
    top_countries(data, m, !!var)
  } else {
    setdiff(top_countries(data, m, !!var), top_countries(data, n-1, !!var))
  }
}
```

```{r}
# Read input data

# https://data.worldbank.org/indicator/SP.POP.TOTL
pop_raw <- read_csv("../analysis/API_SP.POP.TOTL_DS2_en_csv_v2_887275.csv", 
                    skip = 4) %>% 
  select(`Country Name`, `2018`) %>% 
  rename(country = `Country Name`,
         population = `2018`)

time_series_covid19_confirmed_global <- 
  read_csv(paste0("../csse_covid_19_data/csse_covid_19_time_series/",
                  "time_series_covid19_confirmed_global.csv"))

time_series_covid19_deaths_global <- 
  read_csv(paste0("../csse_covid_19_data/csse_covid_19_time_series/",
                  "time_series_covid19_deaths_global.csv"))

# Prepare data

cases <- time_series_covid19_confirmed_global %>% 
  select(-`Province/State`, -Lat, -Long) %>% 
  pivot_longer(-`Country/Region`, 
               names_to = "date", values_to = "cases_cum") %>% 
  rename(country = `Country/Region`) %>% 
  mutate(date = mdy(date)) %>% 
  group_by(country, date) %>% 
  summarize(cases_cum = sum(cases_cum)) %>% 
  mutate(cases_new = cases_cum - lag(cases_cum),
         cases_growth_rate_pct = round(cases_new/lag(cases_cum)*100, 1)) %>% 
  ungroup()

deaths <- time_series_covid19_deaths_global %>% 
  select(-`Province/State`, -Lat, -Long) %>% 
  pivot_longer(-`Country/Region`, 
               names_to = "date", values_to = "deaths_cum") %>% 
  rename(country = `Country/Region`) %>% 
  mutate(date = mdy(date)) %>% 
  group_by(country, date) %>% 
  summarize(deaths_cum = sum(deaths_cum)) %>% 
  mutate(deaths_new = deaths_cum - lag(deaths_cum),
         deaths_growth_rate_pct = round(deaths_new/lag(deaths_cum)*100, 1)) %>% 
  ungroup()

data <- full_join(cases, deaths)

data <- data %>%
  group_by(country) %>% 
  mutate(case_ind = ifelse(cases_cum >= LIMIT_CASE, 1, 0),
         days_since_limit_case = cumsum(case_ind),
         death_ind = ifelse(deaths_cum >= LIMIT_DEATH, 1, 0),
         days_since_limit_death = cumsum(death_ind)) %>% 
  ungroup() %>% 
  select(-case_ind, -death_ind)

mapping <- tibble(
  country = 
    c("Bahamas, The", "Brunei Darussalam", "Myanmar", "Congo, Rep.", 
      "Congo, Dem. Rep.", "Czech Republic", "Diamond Princess", 
      "Egypt, Arab Rep.", "Gambia, The", "Holy See", "Iran, Islamic Rep.", 
      "Korea, Rep.", "Kyrgyz Republic", "Lao PDR", "MS Zaandam", 
      "Russian Federation", "St. Kitts and Nevis", "St. Lucia" , 
      "St. Vincent and the Grenadines", "Slovak Republic", 
      "Syrian Arab Republic", "Taiwan*", "United States", "Venezuela, RB",
      "Western Sahara"),
  country_covid = as.character(setdiff(data$country, pop_raw$country))
)

pop <- full_join(pop_raw, mapping) %>% 
  mutate(country = ifelse(is.na(country_covid), country, country_covid)) %>% 
  select(country, population)

pop$population[pop$country == "Diamond Princess"] <- 3711
pop$population[pop$country == "MS Zaandam"] <- 1829
pop$population[pop$country == "Holy See"] <- 800
pop$population[pop$country == "Taiwan*"] <- 23780452
pop$population[pop$country == "Western Sahara"] <- 567402

data <- left_join(data, pop)

data <- data %>% 
  mutate(cases_cum_per_100k = round(cases_cum/population*100000, 3),
         cases_new_per_100k = round(cases_new/population*100000, 3),
         deaths_cum_per_100k = round(deaths_cum/population*100000, 6),
         deaths_new_per_100k = round(deaths_new/population*100000, 6))

data <- data %>% 
  group_by(country) %>% 
  mutate(case_rate_ind = ifelse(cases_cum_per_100k >= LIMIT_CASE_RATE, 1, 0),
         days_since_limit_case_rate = cumsum(case_rate_ind),
         death_rate_ind = ifelse(deaths_cum_per_100k >= LIMIT_DEATH_RATE, 1, 0),
         days_since_limit_death_rate = cumsum(death_rate_ind)) %>% 
  ungroup() %>% 
  select(-case_rate_ind, -death_rate_ind)

latest_date <- max(cases$date)
```

Global overview
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Global cases and deaths

```{r}
data_sum <- data %>%
  select(date, cases_cum, cases_new, deaths_cum, deaths_new) %>% 
  group_by(date) %>% 
  summarize_all(.funs = sum, na.rm = TRUE)

data_sum %>% 
  arrange(desc(date)) %>% 
  datatable(colnames = c("Date", "Total cases", "New cases",
                         "Total deaths", "New deaths"),
            rownames = FALSE,
            options = list(pageLength = 20))
```

Column {data-width=500}
-----------------------------------------------------------------------

### Global new cases

```{r}
g <- data_sum %>% 
  filter(date >= dmy("01-03-2020")) %>% 
  ggplot(aes(x = date, y = cases_new)) + 
  geom_point(color = "navy") + geom_smooth()

ggplotly(g)
```

### Global new deaths

```{r}
g <- data_sum %>% 
  filter(date >= dmy("01-03-2020")) %>% 
  ggplot(aes(x = date, y = deaths_new)) + 
  geom_point(color = "navy") + geom_smooth()

ggplotly(g)
```

Case overview
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Cases last day

```{r}
data %>% 
  filter(date == latest_date) %>% 
  select(country, cases_cum, cases_new, 
         cases_cum_per_100k, cases_new_per_100k) %>% 
  arrange(desc(cases_new)) %>% 
  datatable(colnames = c("Country", "Total cases", "New cases",
                         "Total cases per 100k", "New cases per 100k"),
            rownames = FALSE,
            options = list(pageLength = 15))
```


Column {data-width=500}
-----------------------------------------------------------------------

### Total cases per country


```{r}
plot_data(data, latest_date, cases_cum)
```

### Total case rate per country

```{r}
data %>% 
  filter(cases_cum >= CASE_CUTOFF) %>% 
  plot_data(latest_date, cases_cum_per_100k)
```


Column {data-width=500}
-----------------------------------------------------------------------

### Total new cases per country

```{r}
plot_data(data, latest_date, cases_new)
```


### Total new case rate per country

```{r}
data %>% 
  filter(cases_cum >= CASE_CUTOFF) %>% 
  plot_data(latest_date, cases_new_per_100k)
```


Death overview
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Deaths last day

```{r}
data %>% 
  filter(date == latest_date) %>% 
  select(country, deaths_cum, deaths_new, 
         deaths_cum_per_100k, deaths_new_per_100k) %>% 
  arrange(desc(deaths_new)) %>% 
  datatable(colnames = c("Country", "Total deaths", "New deaths",
                         "Total deaths per 100k", "New deaths per 100k"),
            rownames = FALSE,
            options = list(pageLength = 15))
```


Column {data-width=500}
-----------------------------------------------------------------------

### Total deaths per country


```{r}
plot_data(data, latest_date, deaths_cum)
```

### Total death rate per country

```{r}
data %>% 
  filter(cases_cum >= CASE_CUTOFF) %>% 
  plot_data(latest_date, deaths_cum_per_100k)
```


Column {data-width=500}
-----------------------------------------------------------------------

### Total new deaths per country

```{r}
plot_data(data, latest_date, deaths_new)
```


### Total new death rate per country

```{r}
data %>% 
  filter(cases_cum >= CASE_CUTOFF) %>% 
  plot_data(latest_date, deaths_new_per_100k)
```

Case trends
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Case trend for top 10 countries

Top 10 countries according to new cases on the last day.

```{r}
data %>% 
  filter(country %in% top_country_range(., 1, 10, cases_new)) %>% 
  plot_trend(days_since_limit_case, cases_cum, MAX_DAYS)
```

### Case trend for top 11-20 countries

```{r}
data %>% 
  filter(country %in% top_country_range(., 11, 20, cases_new)) %>% 
  plot_trend(days_since_limit_case, cases_cum, MAX_DAYS)
```


Column {data-width=500}
-----------------------------------------------------------------------

### Case rate trend for top 10 countries

Top 10 countries according to new case rate on the last days, countries with min. 1000 cases.

```{r}
data %>%  
  group_by(country) %>% 
  filter(max(cases_cum) >= CASE_CUTOFF) %>% 
  ungroup() %>%
  filter(country %in% top_country_range(., 1, 10, cases_new_per_100k)) %>% 
  plot_trend(days_since_limit_case_rate, cases_cum_per_100k, MAX_DAYS)
```

### Case rate trend for top 11-20 countries

```{r}
data %>%   
  group_by(country) %>% 
  filter(max(cases_cum) >= CASE_CUTOFF) %>% 
  ungroup() %>%
  filter(country %in% top_country_range(., 11, 20, cases_new_per_100k)) %>% 
  plot_trend(days_since_limit_case_rate, cases_cum_per_100k, MAX_DAYS)
```

Death trends
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Death trend for top 10 countries

Top 10 countries according to new deaths on the last day.

```{r}
data %>% 
  filter(country %in% top_country_range(., 1, 10, deaths_new)) %>% 
  plot_trend(days_since_limit_death, deaths_cum, MAX_DAYS)
```

### Death trend for top 11-20 countries

```{r}
data %>% 
  filter(country %in% top_country_range(., 11, 20, deaths_new)) %>% 
  plot_trend(days_since_limit_death, deaths_cum, MAX_DAYS)
```


Column {data-width=500}
-----------------------------------------------------------------------

### Death rate trend for top 10 countries

Top 10 countries according to new death rate on the last day, countries with min. 50 deaths.

```{r}
data %>% 
  group_by(country) %>% 
  filter(max(deaths_cum) >= DEATH_CUTOFF) %>% 
  ungroup() %>% 
  filter(country %in% top_country_range(., 1, 10, deaths_new_per_100k)) %>% 
  plot_trend(days_since_limit_death_rate, deaths_cum_per_100k, MAX_DAYS)
```

### Death rate trend for top 11-20 countries

```{r}
data %>% 
  group_by(country) %>% 
  filter(max(deaths_cum) >= DEATH_CUTOFF) %>% 
  ungroup() %>% 
  filter(country %in% top_country_range(., 11, 20, deaths_new_per_100k)) %>% 
  plot_trend(days_since_limit_death_rate, deaths_cum_per_100k, MAX_DAYS)
```
