---
title: "COVID-19 dashboard de Zdendulak"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: flatly
---

```{r setup, include=FALSE}

# Load libraries

library(flexdashboard)
library(readr)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(plotly)
library(DT)

# Load constants

LIMIT_CASE <- 100
LIMIT_DEATH <- 10

LIMIT_CASE_RATE <- 1
LIMIT_DEATH_RATE <- 0.1

CASE_CUTOFF <- 1000
DEATH_CUTOFF <- 50
MAX_DAYS <- 40
SMOOTH_WINDOW <- 7

# Load functions

plot_data <- function(data, date, var, group_var = NULL, n = 20, plotly = T) {
  date_ <- date
  var <- enquo(var)
  group_var <- enquo(group_var)
  levels <- levels(pull(data, !!group_var))
  
  g <- data %>% 
    filter(date == date_) %>% 
    top_n(n, !!var) %>% 
    ggplot(aes(y = reorder(country, !!var), x = !!var, fill = !!group_var)) + 
    geom_bar(stat = "identity") + 
    theme_light() +
    theme(axis.title.y=element_blank(),
          legend.justification = c(1, 0), legend.position = c(0.95, 0.05)) +
    scale_fill_brewer(palette = "Set1", drop = T, limits = levels)
  
  if (plotly) {
    ggplotly(g) %>% 
      layout(legend = list(x = 0.55, y = 0.05))
  } else {
    g
  }
}

plot_trend <- function(data, xvar, yvar, xvar_max = NULL, plotly = TRUE) {
  xvar <- enquo(xvar)
  yvar <- enquo(yvar)
  
  g <- data %>% 
    filter(!!xvar != 0,
           !!xvar <= xvar_max) %>% 
    ggplot(aes(x = !!xvar, y = !!yvar, color = country)) + 
    geom_line() + scale_y_continuous(trans='log10') +
    theme_light()
  
  if (plotly) {
    ggplotly(g)
  } else {
    g
  }
}

plot_map <- function(data, var, legend_title) {
  var <- enquo(var)
  values <- pull(data, !!var)
  
  l <- list(
    color = toRGB("grey"), 
    width = 0.5
  )
  
  geo <- list(
    scope = 'world',
    showframe = FALSE,
    showcoastlines = FALSE,
    projection = list(type = 'robinson'),
    lonaxis = list(range = c(-30, 55)),
    lataxis = list(range = c(35, 70))
  )
  
  map <- plot_geo(data) %>%
    add_trace(
      z = values, color = values, colors = 'Reds',
      text = ~country, locations = ~country_code, marker = list(line = l)
    ) %>% 
    colorbar(title = legend_title) %>% 
    layout(geo = geo)
  
  map
}

top_countries <- function(data, n, var) {
  var <- enquo(var)
  
  data %>% 
    filter(date == latest_date) %>% 
    top_n(n, !!var) %>% 
    pull(country)
}

top_country_range <- function(data, n, m, var) {
  var <- enquo(var)
  
  if (n == 1) {
    top_countries(data, m, !!var)
  } else {
    setdiff(top_countries(data, m, !!var), top_countries(data, n-1, !!var))
  }
}
```

```{r}
# Read input data

# https://data.worldbank.org/indicator/SP.POP.TOTL
pop_raw <- read_csv("../analysis/API_SP.POP.TOTL_DS2_en_csv_v2_887275.csv", 
                    skip = 4) %>% 
  select(`Country Name`, `2018`) %>% 
  rename(country = `Country Name`,
         population = `2018`)

pop_meta <- 
  read_csv(paste0("../analysis/", 
                  "Metadata_Country_API_SP.POP.TOTL_DS2_en_csv_v2_887275.csv")
  ) %>%
  select(country = TableName,
         region = Region, 
         country_code = `Country Code`) %>% 
  mutate(region = as.factor(region))

pop_raw <- pop_raw %>% left_join(pop_meta)

time_series_covid19_confirmed_global <- 
  read_csv(paste0("../csse_covid_19_data/csse_covid_19_time_series/",
                  "time_series_covid19_confirmed_global.csv"))

time_series_covid19_deaths_global <- 
  read_csv(paste0("../csse_covid_19_data/csse_covid_19_time_series/",
                  "time_series_covid19_deaths_global.csv"))

# Prepare data

cases <- time_series_covid19_confirmed_global %>% 
  select(-`Province/State`, -Lat, -Long) %>% 
  pivot_longer(-`Country/Region`, 
               names_to = "date", values_to = "cases_cum") %>% 
  rename(country = `Country/Region`) %>% 
  mutate(date = mdy(date)) %>% 
  arrange(country, date) %>% 
  group_by(country, date) %>% 
  summarize(cases_cum = sum(cases_cum)) %>% 
  mutate(cases_new = cases_cum - dplyr::lag(cases_cum),
         cases_new_smooth = zoo::rollapply(cases_new, SMOOTH_WINDOW, mean, 
                                           align = "center", fill = NA),
         cases_growth_rate_pct = round(cases_new / lag(cases_cum) * 100, 1)) %>% 
  ungroup()

deaths <- time_series_covid19_deaths_global %>% 
  select(-`Province/State`, -Lat, -Long) %>% 
  pivot_longer(-`Country/Region`, 
               names_to = "date", values_to = "deaths_cum") %>% 
  rename(country = `Country/Region`) %>% 
  mutate(date = mdy(date)) %>% 
  arrange(country, date) %>% 
  group_by(country, date) %>% 
  summarize(deaths_cum = sum(deaths_cum)) %>% 
  mutate(deaths_new = deaths_cum - dplyr::lag(deaths_cum),
         deaths_new_smooth = zoo::rollapply(deaths_new, SMOOTH_WINDOW, mean, 
                                            align = "center", fill = NA),
         deaths_growth_rate_pct = round(deaths_new / lag(deaths_cum) * 100, 1)
  ) %>% 
  ungroup()

data <- full_join(cases, deaths)

data <- data %>%
  group_by(country) %>% 
  mutate(case_ind = ifelse(cases_cum >= LIMIT_CASE, 1, 0),
         days_since_limit_case = cumsum(case_ind),
         death_ind = ifelse(deaths_cum >= LIMIT_DEATH, 1, 0),
         days_since_limit_death = cumsum(death_ind)) %>% 
  ungroup() %>% 
  select(-case_ind, -death_ind)

mapping <- tibble(
  country = 
    c("Bahamas, The", "Brunei Darussalam", "Myanmar", "Congo, Rep.", 
      "Congo, Dem. Rep.", "Czech Republic", "Diamond Princess", 
      "Egypt, Arab Rep.", "Gambia, The", "Holy See", "Iran, Islamic Rep.", 
      "Korea, Rep.", "Kyrgyz Republic", "Lao PDR", "MS Zaandam", 
      "Russian Federation", "St. Kitts and Nevis", "St. Lucia" , 
      "St. Vincent and the Grenadines", "Slovak Republic", 
      "Syrian Arab Republic", "Taiwan*", "United States", "Venezuela, RB",
      "Western Sahara", "Yemen, Rep."),
  country_covid = as.character(setdiff(data$country, pop_raw$country))
)

pop <- full_join(pop_raw, mapping) %>% 
  mutate(country = ifelse(is.na(country_covid), country, country_covid)) %>% 
  select(country, country_code, region, population)

pop$population[pop$country == "Diamond Princess"] <- 3711
pop$population[pop$country == "MS Zaandam"] <- 1829
pop$population[pop$country == "Holy See"] <- 800
pop$population[pop$country == "Taiwan*"] <- 23780452
pop$population[pop$country == "Western Sahara"] <- 567402

data <- data %>% 
  left_join(pop)

data <- data %>% 
  mutate(cases_cum_per_100k = round(cases_cum/population*100000, 3),
         cases_new_per_100k = round(cases_new/population*100000, 3),
         cases_new_smooth_per_100k = 
           round(cases_new_smooth/population*100000, 3),
         deaths_cum_per_100k = round(deaths_cum/population*100000, 6),
         deaths_new_per_100k = round(deaths_new/population*100000, 6),
         deaths_new_smooth_per_100k = 
           round(deaths_new_smooth/population*100000, 6))

data <- data %>% 
  group_by(country) %>% 
  mutate(case_rate_ind = ifelse(cases_cum_per_100k >= LIMIT_CASE_RATE, 1, 0),
         days_since_limit_case_rate = cumsum(case_rate_ind),
         death_rate_ind = ifelse(deaths_cum_per_100k >= LIMIT_DEATH_RATE, 1, 0),
         days_since_limit_death_rate = cumsum(death_rate_ind)) %>% 
  ungroup() %>% 
  select(-case_rate_ind, -death_rate_ind)

data <- data %>% 
  filter(!(country %in% c("Diamond Princess", "Holy See", "MS Zaandam")))

latest_date <- max(cases$date)


data_map <- data %>% 
  filter(date == latest_date,
         !(country %in% c("San Marino", "Andorra", "Monaco", "Liechtenstein")))
```


World maps
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Total cases per 100k

```{r}
plot_map(data_map, cases_cum_per_100k, "Total cases per 100k")
```

### New cases per 100k

```{r}
plot_map(data_map, cases_new_per_100k, "New cases per 100k")
```

Column {data-width=500}
-----------------------------------------------------------------------

### Total deaths per 100k

```{r}
plot_map(data_map, deaths_cum_per_100k, "Total deaths per 100k")
```

### New deaths per 100k

```{r}
plot_map(data_map, deaths_new_per_100k, "New deaths per 100k")
```

Global overview
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Global cases and deaths

```{r}
data_sum <- data %>%
  select(date, cases_cum, cases_new, deaths_cum, deaths_new) %>%
  group_by(date) %>%
  summarize_all(.funs = sum, na.rm = TRUE)

data_sum %>%
  arrange(desc(date)) %>%
  datatable(colnames = c("Date", "Total cases", "New cases",
                         "Total deaths", "New deaths"),
            rownames = FALSE,
            options = list(pageLength = 20))
```

Column {data-width=500}
-----------------------------------------------------------------------

### Global new cases

```{r}
g <- data_sum %>%
  filter(date >= dmy("01-03-2020")) %>%
  ggplot(aes(x = date, y = cases_new)) +
  geom_point(color = "navy") + geom_smooth()

ggplotly(g)
```

### Global new deaths

```{r}
g <- data_sum %>%
  filter(date >= dmy("01-03-2020")) %>%
  ggplot(aes(x = date, y = deaths_new)) +
  geom_point(color = "navy") + geom_smooth()

ggplotly(g)
```

Case overview
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Cases last day

```{r}
data %>%
  filter(date == latest_date) %>%
  select(country, cases_cum, cases_new,
         cases_cum_per_100k, cases_new_per_100k) %>%
  arrange(desc(cases_new)) %>%
  datatable(colnames = c("Country", "Total cases", "New cases",
                         "Total cases per 100k", "New cases per 100k"),
            rownames = FALSE,
            options = list(pageLength = 15))
```


Column {data-width=500}
-----------------------------------------------------------------------

### Total cases per country


```{r}
plot_data(data, latest_date, cases_cum, region)
```

### Total cases per capita per country

```{r}
data %>%
  filter(cases_cum >= CASE_CUTOFF) %>%
  plot_data(latest_date, cases_cum_per_100k, region)
```


Column {data-width=500}
-----------------------------------------------------------------------

### Total new cases per country

```{r}
plot_data(data, latest_date, cases_new, region)
```


### Total new cases per capita per country

```{r}
data %>%
  filter(cases_cum >= CASE_CUTOFF) %>%
  plot_data(latest_date, cases_new_per_100k, region)
```


Death overview
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Deaths last day

```{r}
data %>%
  filter(date == latest_date) %>%
  select(country, deaths_cum, deaths_new,
         deaths_cum_per_100k, deaths_new_per_100k) %>%
  arrange(desc(deaths_new)) %>%
  datatable(colnames = c("Country", "Total deaths", "New deaths",
                         "Total deaths per 100k", "New deaths per 100k"),
            rownames = FALSE,
            options = list(pageLength = 15))
```


Column {data-width=500}
-----------------------------------------------------------------------

### Total deaths per country


```{r}
plot_data(data, latest_date, deaths_cum, region)
```

### Total deaths per capita per country

```{r}
data %>%
  filter(cases_cum >= CASE_CUTOFF) %>%
  plot_data(latest_date, deaths_cum_per_100k, region)
```


Column {data-width=500}
-----------------------------------------------------------------------

### Total new deaths per country

```{r}
plot_data(data, latest_date, deaths_new, region)
```


### Total new deaths per capita per country

```{r}
data %>%
  filter(cases_cum >= CASE_CUTOFF) %>%
  plot_data(latest_date, deaths_new_per_100k, region)
```

Total case trends
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Case trend for top 25 countries

Top 25 countries according to new cases on `r latest_date`.

```{r}
data %>%
  filter(country %in% top_country_range(., 1, 25, cases_new)) %>%
  plot_trend(days_since_limit_case, cases_cum, MAX_DAYS)
```

<!-- ### Case trend for top 11-20 countries -->

<!-- ```{r} -->
<!-- data %>% -->
<!--   filter(country %in% top_country_range(., 11, 20, cases_new)) %>% -->
<!--   plot_trend(days_since_limit_case, cases_cum, MAX_DAYS) -->
<!-- ``` -->


Column {data-width=500}
-----------------------------------------------------------------------

### Case per capita trend for top 25 countries

Top 25 countries according to new cases per capita on `r latest_date`, countries with min. `r CASE_CUTOFF` cases.

```{r}
data %>%
  group_by(country) %>%
  filter(max(cases_cum) >= CASE_CUTOFF) %>%
  ungroup() %>%
  filter(country %in% top_country_range(., 1, 25, cases_new_per_100k)) %>%
  plot_trend(days_since_limit_case_rate, cases_cum_per_100k, MAX_DAYS)
```

<!-- ### Case rate trend for top 11-20 countries -->

<!-- ```{r} -->
<!-- data %>% -->
<!--   group_by(country) %>% -->
<!--   filter(max(cases_cum) >= CASE_CUTOFF) %>% -->
<!--   ungroup() %>% -->
<!--   filter(country %in% top_country_range(., 11, 20, cases_new_per_100k)) %>% -->
<!--   plot_trend(days_since_limit_case_rate, cases_cum_per_100k, MAX_DAYS) -->
<!-- ``` -->

New case trends
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### New case trend for top 25 countries

Top 25 countries according to new cases on `r latest_date`.

```{r}
data %>%
  filter(country %in% top_country_range(., 1, 25, cases_new)) %>%
  plot_trend(days_since_limit_case, cases_new_smooth, MAX_DAYS)
```

<!-- ### New case trend for top 11-20 countries -->

<!-- ```{r} -->
<!-- data %>% -->
<!--   filter(country %in% top_country_range(., 11, 20, cases_new)) %>% -->
<!--   plot_trend(days_since_limit_case, cases_new_smooth, MAX_DAYS) -->
<!-- ``` -->


Column {data-width=500}
-----------------------------------------------------------------------

### New cases per capita trend for top 25 countries

Top 25 countries according to new cases per capita on `r latest_date`, countries with min. `r CASE_CUTOFF` cases.

```{r}
data %>%
  group_by(country) %>%
  filter(max(cases_cum) >= CASE_CUTOFF) %>%
  ungroup() %>%
  filter(country %in% top_country_range(., 1, 25, cases_new_per_100k)) %>%
  plot_trend(days_since_limit_case_rate, cases_new_smooth_per_100k, MAX_DAYS)
```

<!-- ### New case rate trend for top 11-20 countries -->

<!-- ```{r} -->
<!-- data %>% -->
<!--   group_by(country) %>% -->
<!--   filter(max(cases_cum) >= CASE_CUTOFF) %>% -->
<!--   ungroup() %>% -->
<!--   filter(country %in% top_country_range(., 11, 20, cases_new_per_100k)) %>% -->
<!--   plot_trend(days_since_limit_case_rate, cases_new_smooth_per_100k, MAX_DAYS) -->
<!-- ``` -->

Total death trends
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Death trend for top 25 countries

Top 25 countries according to new deaths on `r latest_date`.

```{r}
data %>%
  filter(country %in% top_country_range(., 1, 25, deaths_new)) %>%
  plot_trend(days_since_limit_death, deaths_cum, MAX_DAYS)
```

<!-- ### Death trend for top 11-20 countries -->

<!-- ```{r} -->
<!-- data %>% -->
<!--   filter(country %in% top_country_range(., 11, 20, deaths_new)) %>% -->
<!--   plot_trend(days_since_limit_death, deaths_cum, MAX_DAYS) -->
<!-- ``` -->


Column {data-width=500}
-----------------------------------------------------------------------

### Deaths per capita trend for top 25 countries

Top 25 countries according to new deaths per capita on `r latest_date`, countries with min. `r DEATH_CUTOFF` deaths.

```{r}
data %>%
  group_by(country) %>%
  filter(max(deaths_cum) >= DEATH_CUTOFF) %>%
  ungroup() %>%
  filter(country %in% top_country_range(., 1, 25, deaths_new_per_100k)) %>%
  plot_trend(days_since_limit_death_rate, deaths_cum_per_100k, MAX_DAYS)
```

<!-- ### Death rate trend for top 11-20 countries -->

<!-- ```{r} -->
<!-- data %>% -->
<!--   group_by(country) %>% -->
<!--   filter(max(deaths_cum) >= DEATH_CUTOFF) %>% -->
<!--   ungroup() %>% -->
<!--   filter(country %in% top_country_range(., 11, 20, deaths_new_per_100k)) %>% -->
<!--   plot_trend(days_since_limit_death_rate, deaths_cum_per_100k, MAX_DAYS) -->
<!-- ``` -->

New death trends
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### New death trend for top 25 countries

Top 25 countries according to new deaths on `r latest_date`.

```{r}
data %>%
  filter(country %in% top_country_range(., 1, 25, deaths_new)) %>%
  plot_trend(days_since_limit_death, deaths_new_smooth, MAX_DAYS)
```

<!-- ### New death trend for top 11-20 countries -->

<!-- ```{r} -->
<!-- data %>% -->
<!--   filter(country %in% top_country_range(., 11, 20, deaths_new)) %>% -->
<!--   plot_trend(days_since_limit_death, deaths_new_smooth, MAX_DAYS) -->
<!-- ``` -->


Column {data-width=500}
-----------------------------------------------------------------------

### New deaths per capita trend for top 25 countries

Top 25 countries according to new deaths per capita on `r latest_date`, countries with min. `r DEATH_CUTOFF` deaths.

```{r}
data %>%
  group_by(country) %>%
  filter(max(deaths_cum) >= DEATH_CUTOFF) %>%
  ungroup() %>%
  filter(country %in% top_country_range(., 1, 25, deaths_new_per_100k)) %>%
  plot_trend(days_since_limit_death_rate, deaths_new_smooth_per_100k, MAX_DAYS)
```

<!-- ### New death rate trend for top 11-20 countries -->

<!-- ```{r} -->
<!-- data %>% -->
<!--   group_by(country) %>% -->
<!--   filter(max(deaths_cum) >= DEATH_CUTOFF) %>% -->
<!--   ungroup() %>% -->
<!--   filter(country %in% top_country_range(., 11, 20, deaths_new_per_100k)) %>% -->
<!--   plot_trend(days_since_limit_death_rate, deaths_new_smooth_per_100k, MAX_DAYS) -->
<!-- ``` -->
