---
title: "COVID-19 dashboard de Zdendulak"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: flatly
  runtime: shiny
---

```{r setup, include=FALSE}

# Load libraries

library(flexdashboard)
library(readr)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(plotly)
library(DT)
library(shiny)
# library(trelliscopejs)
# library(scales)

# Load constants

LIMIT_CASE <- 100
LIMIT_DEATH <- 10

LIMIT_CASE_RATE <- 10
LIMIT_DEATH_RATE <- 1

CASE_CUTOFF <- 1000
DEATH_CUTOFF <- 50
SMOOTH_WINDOW <- 7

# Load functions

plot_data <- function(data, date, var, group_var = NULL, n = 20, plotly = T) {
  date_ <- date
  var <- enquo(var)
  group_var <- enquo(group_var)
  levels <- levels(pull(data, !!group_var))
  
  if (!is.null(date_)) {
    data <- filter(data, date == date_)
  }
  
  g <- data %>% 
    top_n(n, !!var) %>% 
    slice(1:n) %>% # guarantee of the row cutoff
    ggplot(aes(y = reorder(country, !!var), x = !!var, fill = !!group_var)) + 
    geom_bar(stat = "identity") + 
    theme_light() +
    theme(axis.title.y=element_blank(),
          legend.justification = c(1, 0), legend.position = c(0.95, 0.05),
          legend.title = element_blank()) +
    scale_fill_brewer(palette = "Set1", drop = T, limits = levels)
  
  if (plotly) {
    ggplotly(g) %>% 
      layout(legend = list(x = 0.5, y = 0.05))
  } else {
    g
  }
}

plot_trend <- function(data, xvar, yvar, xvar_max = NULL, plotly = TRUE) {
  xvar <- enquo(xvar)
  yvar <- enquo(yvar)
  
  g <- data %>% 
    filter(!!xvar != 0,
           !!xvar <= xvar_max) %>% 
    ggplot(aes(x = !!xvar, y = !!yvar, color = country)) + 
    geom_line() + scale_y_continuous(trans='log10') +
    theme_light()
  
  if (plotly) {
    ggplotly(g)
  } else {
    g
  }
}

plot_map <- function(data, var, legend_title) {
  var <- enquo(var)
  values <- pull(data, !!var)
  
  l <- list(
    color = toRGB("grey"), 
    width = 0.5
  )
  
  geo <- list(
    scope = 'world',
    showframe = FALSE,
    showcoastlines = FALSE,
    projection = list(type = 'robinson'),
    lonaxis = list(range = c(-30, 55)),
    lataxis = list(range = c(35, 70))
  )
  
  map <- plot_geo(data) %>%
    add_trace(
      z = values, color = values, colors = 'Reds',
      text = ~country, locations = ~country_code, marker = list(line = l)
    ) %>% 
    colorbar(title = legend_title) %>% 
    layout(geo = geo)
  
  map
}

top_countries <- function(data, n, var) {
  var <- enquo(var)
  
  data %>% 
    filter(date == latest_date) %>% 
    top_n(n, !!var) %>% 
    pull(country)
}

top_country_range <- function(data, n, m, var) {
  var <- enquo(var)
  
  if (n == 1) {
    top_countries(data, m, !!var)
  } else {
    setdiff(top_countries(data, m, !!var), top_countries(data, n-1, !!var))
  }
}

geo_mean <- function(x) {
  exp(mean(log(x)))
}
```

```{r}
# Read input data

if (interactive()) {
  root <- "./"
} else {
  root <- "../"
}

# https://data.worldbank.org/indicator/SP.POP.TOTL
pop_raw <- 
  read_csv(
    file.path(root, "analysis/API_SP.POP.TOTL_DS2_en_csv_v2_887275.csv"), 
    skip = 4
  ) %>% 
  select(`Country Name`, `2018`) %>% 
  rename(country = `Country Name`,
         population = `2018`)

pop_meta <- 
  read_csv(
    file.path(root, "analysis/", 
              "Metadata_Country_API_SP.POP.TOTL_DS2_en_csv_v2_887275.csv")
  ) %>%
  select(country = TableName,
         region = Region, 
         country_code = `Country Code`) %>% 
  mutate(region = as.factor(region))

pop_raw <- pop_raw %>% left_join(pop_meta)

time_series_covid19_confirmed_global <- 
  read_csv(file.path(root, "csse_covid_19_data/csse_covid_19_time_series/",
                     "time_series_covid19_confirmed_global.csv"))

time_series_covid19_deaths_global <- 
  read_csv(file.path(root, "csse_covid_19_data/csse_covid_19_time_series/",
                     "time_series_covid19_deaths_global.csv"))

time_series_covid19_recovered_global <- 
  read_csv(file.path(root, "csse_covid_19_data/csse_covid_19_time_series/",
                     "time_series_covid19_recovered_global.csv"))

# Prepare data

cases <- time_series_covid19_confirmed_global %>% 
  select(-`Province/State`, -Lat, -Long) %>% 
  pivot_longer(-`Country/Region`, 
               names_to = "date", values_to = "cases_cum") %>% 
  rename(country = `Country/Region`) %>% 
  mutate(date = mdy(date)) %>% 
  arrange(country, date) %>% 
  group_by(country, date) %>% 
  summarize(cases_cum = sum(cases_cum)) %>% 
  mutate(cases_new = cases_cum - dplyr::lag(cases_cum),
         cases_new_smooth = zoo::rollapply(cases_new, SMOOTH_WINDOW, mean, 
                                           align = "right", fill = NA),
         cases_daily_growth_rate_pct = 
           round(cases_new / lag(cases_cum) * 100, 1),
         cases_3day_growth_rate_pct = round(
           (zoo::rollapply(cases_new, 3, sum, align = "right", fill = NA)) /
             lag(cases_cum, 3) * 100, 1)) %>% 
  ungroup()

deaths <- time_series_covid19_deaths_global %>% 
  select(-`Province/State`, -Lat, -Long) %>% 
  pivot_longer(-`Country/Region`, 
               names_to = "date", values_to = "deaths_cum") %>% 
  rename(country = `Country/Region`) %>% 
  mutate(date = mdy(date)) %>% 
  arrange(country, date) %>% 
  group_by(country, date) %>% 
  summarize(deaths_cum = sum(deaths_cum)) %>% 
  mutate(deaths_new = deaths_cum - dplyr::lag(deaths_cum),
         deaths_new_smooth = zoo::rollapply(deaths_new, SMOOTH_WINDOW, mean, 
                                            align = "right", fill = NA),
         deaths_daily_growth_rate_pct = 
           round(deaths_new / lag(deaths_cum) * 100, 1),
         deaths_3day_growth_rate_pct = round(
           (zoo::rollapply(deaths_new, 3, sum, align = "right", fill = NA)) /
             lag(deaths_cum, 3) * 100, 1)) %>%  
  ungroup()

recovered <- time_series_covid19_recovered_global %>% 
  select(-`Province/State`, -Lat, -Long) %>% 
  pivot_longer(-`Country/Region`, 
               names_to = "date", values_to = "recovered_cum") %>% 
  rename(country = `Country/Region`) %>% 
  mutate(date = mdy(date)) %>% 
  arrange(country, date) %>% 
  group_by(country, date) %>% 
  summarize(recovered_cum = sum(recovered_cum)) %>% 
  mutate(recovered_new = recovered_cum - dplyr::lag(recovered_cum),
         recovered_new_smooth = 
           zoo::rollapply(recovered_new, SMOOTH_WINDOW, mean, 
                          align = "right", fill = NA)) %>% 
  ungroup()

data <- cases %>% 
  full_join(deaths) %>% 
  full_join(recovered)

data <- data %>%
  group_by(country) %>% 
  mutate(case_ind = ifelse(cases_cum >= LIMIT_CASE, 1, 0),
         days_since_limit_case = cumsum(case_ind),
         death_ind = ifelse(deaths_cum >= LIMIT_DEATH, 1, 0),
         days_since_limit_death = cumsum(death_ind)) %>% 
  ungroup() %>% 
  select(-case_ind, -death_ind)

mapping <- tibble(
  country = 
    c("Bahamas, The", "Brunei Darussalam", "Myanmar", "Congo, Rep.", 
      "Congo, Dem. Rep.", "Czech Republic", "Diamond Princess", 
      "Egypt, Arab Rep.", "Gambia, The", "Holy See", "Iran, Islamic Rep.", 
      "Korea, Rep.", "Kyrgyz Republic", "Lao PDR", "MS Zaandam", 
      "Russian Federation", "St. Kitts and Nevis", "St. Lucia" , 
      "St. Vincent and the Grenadines", "Slovak Republic", 
      "Syrian Arab Republic", "Taiwan*", "United States", "Venezuela, RB",
      "Western Sahara", "Yemen, Rep."),
  country_covid = as.character(setdiff(data$country, pop_raw$country))
)

pop <- full_join(pop_raw, mapping) %>% 
  mutate(country = ifelse(is.na(country_covid), country, country_covid)) %>% 
  select(country, country_code, region, population)

pop$population[pop$country == "Diamond Princess"] <- 3711
pop$population[pop$country == "MS Zaandam"] <- 1829
pop$population[pop$country == "Holy See"] <- 800
pop$population[pop$country == "Taiwan*"] <- 23780452
pop$population[pop$country == "Western Sahara"] <- 567402

data <- data %>% 
  left_join(pop)

data <- data %>% 
  mutate(cases_cum_per_mil = round(cases_cum/population*1000000, 0),
         cases_new_per_mil = round(cases_new/population*1000000, 1),
         cases_new_smooth_per_mil = 
           round(cases_new_smooth/population*1000000, 1),
         deaths_cum_per_mil = round(deaths_cum/population*1000000, 1),
         deaths_new_per_mil = round(deaths_new/population*1000000, 2),
         deaths_new_smooth_per_mil = 
           round(deaths_new_smooth/population*1000000, 2),
         recovered_cum_per_mil = round(recovered_cum/population*1000000, 0),
         recovered_new_per_mil = round(recovered_new/population*1000000, 1),
         recovered_new_smooth_per_mil = 
           round(recovered_new_smooth/population*1000000, 1))

data <- data %>% 
  group_by(country) %>% 
  mutate(case_rate_ind = ifelse(cases_cum_per_mil >= LIMIT_CASE_RATE, 1, 0),
         days_since_limit_case_rate = cumsum(case_rate_ind),
         death_rate_ind = ifelse(deaths_cum_per_mil >= LIMIT_DEATH_RATE, 1, 0),
         days_since_limit_death_rate = cumsum(death_rate_ind)) %>% 
  ungroup() %>% 
  select(-case_rate_ind, -death_rate_ind)

data <- data %>% 
  filter(!(country %in% c("Diamond Princess", "Holy See", "MS Zaandam")))

latest_date <- max(cases$date)

data_sum <- data %>%
  select(date, cases_cum, cases_new, deaths_cum, deaths_new,
         recovered_cum, recovered_new) %>%
  group_by(date) %>%
  summarize_all(.funs = sum, na.rm = TRUE) %>% 
  mutate(cases_new_smooth = zoo::rollapply(
    cases_new, SMOOTH_WINDOW, mean, align = "right", fill = NA),
    deaths_new_smooth = zoo::rollapply(
      deaths_new, SMOOTH_WINDOW, mean, align = "right", fill = NA),
    recovered_new_smooth = zoo::rollapply(
      recovered_new, SMOOTH_WINDOW, mean, align = "right", fill = NA))

data_map <- data %>% 
  filter(date == latest_date,
         !(country %in% c("San Marino", "Andorra", "Monaco", "Liechtenstein")))
```


<!-- World maps -->
<!-- ======================================================================= -->

<!-- Column {data-width=500} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ### Total cases per mil -->

<!-- ```{r} -->
<!-- plot_map(data_map, cases_cum_per_mil, "Total cases per mil") -->
<!-- ``` -->

<!-- ### New cases per mil -->

<!-- ```{r} -->
<!-- plot_map(data_map, cases_new_per_mil, "New cases per mil") -->
<!-- ``` -->

<!-- Column {data-width=500} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ### Total deaths per mil -->

<!-- ```{r} -->
<!-- plot_map(data_map, deaths_cum_per_mil, "Total deaths per mil") -->
<!-- ``` -->

<!-- ### New deaths per mil -->

<!-- ```{r} -->
<!-- plot_map(data_map, deaths_new_per_mil, "New deaths per mil") -->
<!-- ``` -->

Global overview
=======================================================================

Column {data-width=600}
-----------------------------------------------------------------------

### Global cases and deaths

```{r}
data_sum %>%
  arrange(desc(date)) %>%
  select(date, cases_cum, cases_new, deaths_cum, deaths_new,
         recovered_cum, recovered_new) %>% 
  datatable(colnames = c("Date", "Total cases", "New cases",
                         "Total deaths", "New deaths",
                         "Total recovered", "New recovered"),
            rownames = FALSE,
            options = list(pageLength = 20))
```

Column {data-width=400}
-----------------------------------------------------------------------

### Global new cases

```{r}
g <- data_sum %>%
  filter(date >= dmy("01-03-2020")) %>%
  ggplot(aes(x = date)) +
  geom_col(aes(y = cases_new), fill = "darkturquoise") +
  geom_line(aes(y = dplyr::lead(cases_new_smooth, 3)), color = "blue") +
  theme_light()

ggplotly(g)
```

### Global new deaths

```{r}
g <- data_sum %>%
  filter(date >= dmy("01-03-2020")) %>%
  ggplot(aes(x = date)) +
  geom_col(aes(y = deaths_new), fill = "coral") +
  geom_line(aes(y = dplyr::lead(deaths_new_smooth, 3)), color = "red") +
  theme_light()

ggplotly(g)
```

### Global new recovered

```{r}
g <- data_sum %>%
  filter(date >= dmy("01-03-2020")) %>%
  ggplot(aes(x = date)) +
  geom_col(aes(y = recovered_new), fill = "aquamarine") +
  geom_line(aes(y = dplyr::lead(recovered_new_smooth, 3)), color = "darkgreen") +
  theme_light()

ggplotly(g)
```

Daily overview
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------
```{r}
region_opts <- as.character(unique(data$region))

dateInput("date", label = "Select date:", value = latest_date,
          max = latest_date, format = "dd/mm/yyyy")

selectInput("metric", label = "Select metric:",
            choices = c("Cases", "Deaths", "Recovered"), 
            selected = "Cases")

checkboxInput("smoothed", "Smooth new", FALSE)

selectInput("region", label = "Select region:", 
            choices = c("All", region_opts), selected = "All")

sliderInput("nbars", label = "Countries to plot:",
            min = 5, max = 30, value = 20, step = 5)

sliderInput("cutoff", label = "Select case lower bound:",
            min = 0, max = 1000, value = 1000, step = 100)
```

```{r}
data_last <- reactive({
  tmp <- if (input$region == "All") {
    data
  } else {
    data %>% filter(region == input$region)
  }
  
  filter(tmp, cases_cum >= input$cutoff)
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### Table overview

```{r}
renderDT({
  if (input$metric == "Cases") {
    data_last() %>%
      filter(date == input$date) %>%
      select(country, cases_cum, cases_new,
             cases_cum_per_mil, cases_new_per_mil) %>%
      arrange(desc(cases_cum)) %>%
      datatable(colnames = c("Country", "Total cases", "New cases",
                             "Total cases per mil", "New cases per mil"),
                rownames = FALSE,
                options = list(pageLength = 15))
  } else if (input$metric == "Deaths") {
    data_last() %>%
      filter(date == input$date) %>%
      select(country, deaths_cum, deaths_new,
             deaths_cum_per_mil, deaths_new_per_mil) %>%
      arrange(desc(deaths_cum)) %>%
      datatable(colnames = c("Country", "Total deaths", "New deaths",
                             "Total deaths per mil", "New deaths per mil"),
                rownames = FALSE,
                options = list(pageLength = 15))
  } else if (input$metric == "Recovered") {
    data_last() %>%
      filter(date == input$date) %>%
      select(country, recovered_cum, recovered_new,
             recovered_cum_per_mil, recovered_new_per_mil) %>%
      arrange(desc(recovered_cum)) %>%
      datatable(colnames = c("Country", "Total recovered", "New recovered",
                             "Total recovered per mil", "New recovered per mil"),
                rownames = FALSE,
                options = list(pageLength = 15)) 
  }
})
```


Column {data-width=500}
-----------------------------------------------------------------------

### Total per country


```{r}
renderPlotly({
  plotvar <- if (input$metric == "Cases") {
    quo(cases_cum)
  } else if (input$metric == "Deaths") {
    quo(deaths_cum)
  } else if (input$metric == "Recovered"){
    quo(recovered_cum)
  }
  
  plot_data(data_last(), input$date, !!plotvar, region, input$nbars)
})
```

### Total per million per country

```{r}
renderPlotly({
  plotvar <- if (input$metric == "Cases") {
    quo(cases_cum_per_mil)
  } else if (input$metric == "Deaths") {
    quo(deaths_cum_per_mil)
  } else if (input$metric == "Recovered"){
    quo(recovered_cum_per_mil)
  }
  
  plot_data(data_last(), input$date, !!plotvar, region, input$nbars)
})
```


Column {data-width=500}
-----------------------------------------------------------------------

### New per country

```{r}
renderPlotly({
  plotvar <- if (input$metric == "Cases" & input$smoothed == FALSE) {
    quo(cases_new) 
  } else if (input$metric == "Cases" & input$smoothed == TRUE) {
    quo(cases_new_smooth)
  } else if (input$metric == "Deaths" & input$smoothed == FALSE) {
    quo(deaths_new)
  } else if (input$metric == "Deaths" & input$smoothed == TRUE) {
    quo(deaths_new_smooth)
  } else if (input$metric == "Recovered" & input&smoothed == FALSE){
    quo(recovered_new)
  } else if (input$metric == "Recovered" & input&smoothed == TRUE){
    quo(recovered_new_smooth)
  }
  
  plot_data(data_last(), input$date, !!plotvar, region, input$nbars)
})
```


### New per million per country

```{r}
renderPlotly({
  plotvar <- if (input$metric == "Cases" & input$smoothed == FALSE) {
    quo(cases_new_per_mil)
  } else if (input$metric == "Cases" & input$smoothed == TRUE) {
    quo(cases_new_smooth_per_mil)
  } else if (input$metric == "Deaths" & input$smoothed == FALSE) {
    quo(deaths_new_per_mil)
  } else if (input$metric == "Deaths" & input$smoothed == TRUE) {
    quo(deaths_new_smooth_per_mil)
  } else if (input$metric == "Recovered" & input$smoothed == FALSE){
    quo(recovered_new_per_mil)
  } else if (input$metric == "Recovered" & input$smoothed == TRUE){
    quo(recovered_new_smooth_per_mil)
  }
  
  plot_data(data_last(), input$date, !!plotvar, region, input$nbars)
})
```








Trends
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
selectInput("metric2", label = "Select metric:",
            choices = c("Total cases", "New cases",
                        "Total deaths", "New deaths"), 
            selected = "Total cases")

selectInput("region2", label = "Select region:", 
            choices = c("All", region_opts), selected = "All")

selectInput("subset", label = "Select subset:",
            choices = c("Top cummulative", "Top cumm. per million",
                        "Top new", "Top new per million", "Top growth"),
            selected = "Top cummulative")

sliderInput("maxdays", label = "Maximum days to plot:",
            min = 120, max = 200, value = 150, step = 10)

sliderInput("nlines", label = "Countries to plot:",
            min = 5, max = 30, value = 20, step = 5)

sliderInput("cutoff2", label = "Select case lower bound:",
            min = 0, max = 1000, value = 1000, step = 100)

sliderInput("cutoff3", label = "Select death lower bound:",
            min = 0, max = 100, value = 100, step = 10)
```


```{r}
data_trend <- reactive({
  tmp <- if (input$region2 == "All") {
    data
  } else {
    data %>% filter(region == input$region2)
  }
  
  tmp %>%
    group_by(country) %>%
    filter(max(cases_cum) >= input$cutoff2,
           max(deaths_cum) >= input$cutoff3) %>%
    ungroup()
})

data_trend_cases <- reactive({
  plotvar <- if(input$subset == "Top cummulative") {
    quo(cases_cum)
  } else if (input$subset == "Top cumm. per million") {
    quo(cases_cum_per_mil)
  } else if (input$subset == "Top new") {
    quo(cases_new)
  } else if (input$subset == "Top new per million") {
    quo(cases_new_per_mil)
  } else if (input$subset == "Top growth") {
    quo(cases_3day_growth_rate_pct)
  }
  
  data_trend() %>% 
      filter(country %in% top_countries(., input$nlines, !!plotvar))
})

data_trend_deaths <- reactive({
  plotvar <- if(input$subset == "Top cummulative") {
    quo(deaths_cum)
  } else if (input$subset == "Top cumm. per million") {
    quo(deaths_cum_per_mil)
  } else if (input$subset == "Top new") {
    quo(deaths_new)
  } else if (input$subset == "Top new per million") {
    quo(deaths_new_per_mil)
  } else if (input$subset == "Top growth") {
    quo(deaths_3day_growth_rate_pct)
  }
  
  data_trend() %>% 
    filter(country %in% top_countries(., input$nlines, !!plotvar))
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### Trend for top countries

Top countries according to the selected subset on `r latest_date`.

```{r}
renderPlotly({
  if (input$metric2 == "Total cases") {
    data_trend_cases() %>%
      plot_trend(days_since_limit_case, cases_cum, input$maxdays)
  } else if (input$metric2 == "New cases") {
    data_trend_cases() %>%
      plot_trend(days_since_limit_case, cases_new_smooth, input$maxdays)
  } else if (input$metric2 == "Total deaths") {
    data_trend_deaths() %>%
      plot_trend(days_since_limit_death, deaths_cum, input$maxdays)
  } else if (input$metric2 == "New deaths") {
    data_trend_deaths() %>%
      plot_trend(days_since_limit_death, deaths_new_smooth, input$maxdays)
  }
})
```

<!-- ### Time slice view -->

<!-- ```{r} -->
<!-- renderPlotly({ -->
<!--   data_trend_cases() %>%  -->
<!--     filter(days_since_limit_case == 45) %>%  -->
<!--     plot_data(date = NULL, var = cases_cum, group_var = region, n = input$nlines) -->
<!-- }) -->
<!-- ``` -->


Column {data-width=500}
-----------------------------------------------------------------------

### Trend per million for top countries

Top countries according to the selected subset per million on `r latest_date`.

```{r}
renderPlotly({
  if (input$metric2 == "Total cases") {
    data_trend_cases() %>%
      plot_trend(days_since_limit_case_rate, cases_cum_per_mil, input$maxdays)
  } else if (input$metric2 == "New cases") {
    data_trend_cases() %>%
      plot_trend(days_since_limit_case_rate, cases_new_smooth_per_mil, input$maxdays)
  } else if (input$metric2 == "Total deaths") {
    data_trend_deaths() %>%
      plot_trend(days_since_limit_death_rate, deaths_cum_per_mil, input$maxdays)
  } else if (input$metric2 == "New deaths") {
    data_trend_deaths() %>%
      plot_trend(days_since_limit_death_rate, deaths_new_smooth_per_mil, input$maxdays)
  }
})
```

<!-- Cases by country -->
<!-- ======================================================================= -->

<!-- ```{r} -->
<!-- data %>% -->
<!--   group_by(country) %>% -->
<!--   filter(max(cases_cum) >= 10000) %>% -->
<!--   mutate(cases_new = scales::squish(cases_new, -->
<!--                             quantile(cases_new, c(.01, .99), na.rm = T)), -->
<!--          deaths_new = scales::squish(deaths_new, -->
<!--                              quantile(deaths_new, c(.01, .99), na.rm = T))) %>% -->
<!--   ungroup() %>% -->
<!--   filter(date >= dmy("01-03-2020")) %>% -->
<!--   select(country, date, cases_new, cases_new_smooth, cases_cum, -->
<!--          deaths_new, deaths_new_smooth, deaths_cum) %>% -->
<!--   ggplot(aes(x = date)) + -->
<!--   geom_col(aes(y = cases_new), fill = "darkturquoise") + -->
<!--   # geom_col(aes(y = deaths_new), fill = "orangered") + -->
<!--   geom_line(aes(y = dplyr::lead(cases_new_smooth, 3)), color = "blue", size = 1) + -->
<!--   # geom_line(aes(y = dplyr::lead(deaths_new_smooth, 3)), color = "red", size = 1) + -->
<!--   facet_trelliscope( -->
<!--     ~ country, nrow = 2, ncol = 4, scales = c("same", "free"), as_plotly = F, -->
<!--     path = "www/trelli", name = "Statistics by country", -->
<!--     desc = "Daily counts with 7-day rolling average", -->
<!--     state = list(sort = list(sort_spec("cases_cum_max", dir = "desc"))) -->
<!--   ) -->
<!-- ``` -->
